Motional Quantum Ground-State Cooing Outside the Lamb-Dicke Regime

### 2017-06-21 paper.tex
More detail description of sequence construction and optimizations

Taking all these features of our system into account, we use a Monte-Carlo simulation to verify
the validity of our method \fxnote{WRITE BRIEF SUMMARY IN APPENDIX?}.
In the simulation, we can observe the high heating rate due to the high Lamb-Dicke parameters
and confirm that by using high order Raman sideband transition in the cooling sequence we can
suppress this effect and reduces the motional energy of the atom faster.
The simulation is also used to guide the optimization of the cooling sequence by exploring the
large parameter space and finding a robust cooling strategy. As shown in figure \ref{f-setup}C,
we found that instead of cooling on only one sideband order at a time, it is generally more
efficient to alternate the cooling pulse between two neighboring orders (axial) or pulse lengths.
A cooling sequence like this minimizes the accumulation of atom in a state not addressed by a
particular Raman pulse parameter.

>>>>

Taking all these features of our system into account, we use a Monte-Carlo simulation to verify
the validity of our method \fxnote{WRITE BRIEF SUMMARY IN APPENDIX?}.
In the simulation, we can observe the high heating rate due to the high Lamb-Dicke parameters
and confirm that by using high order Raman sideband transition in the cooling sequence we can
suppress this effect and reduces the motional energy of the atom faster.
The simulation is also used to guide the optimization of the cooling sequence by exploring the
large parameter space and finding a robust cooling strategy.
As shown in figure \ref{f-setup}C, we found that instead of cooling on only one sideband order
at a time, it is generally more efficient to alternate the cooling pulse between two
neighboring orders (axial) to minimize the accumulation of atom in a state
not addressed by a particular order.
The simulation also shows that the most efficient way of cooling on a high order sideband is
to perform a $\pi$ pulse corresponding to its maximum matrix element.
This makes sure we are using each order to cool a range of states that has the strongest
coupling to this order and let other sidebands to cool other states.
This strategy is only not as effective during the last stage of cooling in each direction
where most of the remainly excited population is in the first motional excited state
while the rest also have the strongest coupling to the first cooling sideband.
Because of this, we switch to cooling only on the first order sideband as the last cooling
stage while maintaining the alternating order between different axis to maximize the final
ground state probability.
Guided by the simulation result, we construct our initial cooling sequence by first starting
at the highest two observed cooling sideband and decrease the order after cooling on them
for 6 to 15 cycles with the optimum pulse lengths.
This sequence gives good cooling performance which is then experimentally further optimized
by fine tuning of different parameters.
